---
title: "Practice Visual Priming"
author: "Dave Yachabach"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(data.table)
require(ggplot2)
```

## Practice Statistical Analysis for Visual Priming Experiment

This document describes a statistical analysis of simulated data.  The data simulates the performance of airline crews flying approach scenarios in a Level D 737 flight simulator.  For a description of the experiment see *Rethinking Runway Safety from the Bottom Up*.  See the codebook for a description of variables and tables.  


## Data Description  
The operational data for this practice analysis is in a practice data file.  The available files are:  

- *PD_4-22-2021.csv*.  

The simulated Roster data is in a Roster file.  The available files are:  

- *Roster_4-21-2021*  

```{r LoadData, echo=FALSE}

pthData <- "C:/Users/yacha/OneDrive/Education/Personal Interests/Aviation Research Interests/Visual Priming Experiment/Software/Practice Visual Priming Analysis/Data/"

filData <- paste(pthData,"PD_4-22-2021.csv", sep = "")
dt <- fread(filData, skip = 1, blank.lines.skip = TRUE, check.names = TRUE)

filData <- paste(pthData,"Roster_4-21-2021.csv", sep = "")
dtRoster <- fread(filData, skip = 1, blank.lines.skip = TRUE, check.names = TRUE)

```

### Independence of RunIDs  
The following graphs indicate that RunIDs were evenly distributed throughout a simulator session.  In other words, RL-NI was just as likely to occur on the 6th run as on the 15th run.



```{r RunID_Independence, echo=FALSE}

dtPlot = dt[,.(Run.ID,Run)]

g <- ggplot(dtPlot)
gg <- g+geom_density(aes(x = Run, fill=Run.ID , color=Run.ID ),alpha = 0.10)

gg + labs(title = "Frequency of RunIDs in Run Sequence", 
          subtitle = paste(" (N=", dtPlot[,.N]," Runs)",sep=""), 
          x = "Run Number", y = "Density", fill = "")

```

### Landing Accuracy  
Starting with landing accuracy, we will show the frequency distribution of the population separted by treatment and  control.  

```{r Xtd_Frequency_Distribution, echo=FALSE}

dtPlot = dt[Go.Around.==FALSE,.(Xtd, Treatment)]

g <- ggplot(dtPlot)
gg <- g+geom_histogram(aes(x = Xtd, fill = Treatment), bins=20,alpha = 0.25, position = "dodge")
gg <- gg+geom_freqpoly(aes(x = Xtd, color = Treatment), bins=20,alpha = 0.25, position = "dodge", size = 2, show.legend = FALSE)
gg <- gg+geom_vline(xintercept = mean(dtPlot[Treatment=="Control",Xtd]), color = "red", size = 2, alpha=.25)
gg <- gg+geom_vline(xintercept = mean(dtPlot[Treatment=="Treatment",Xtd]), color = "lightblue", size = 2, alpha=.5)
gg + labs(title = "Frequency of Landing Location (Xtd)", 
          subtitle = paste(" (N=", dtPlot[,.N]," Runs)",sep=""), 
          x = "Xtd", y = "Frequency", fill = "")


```

It's a little easier to see the decrease in variance between treatment and control with a density distribution.


```{r Xtd_Density_Distribution, echo=FALSE}

dtPlot = dt[Go.Around.==FALSE,.(Xtd, Treatment)]

g <- ggplot(dtPlot)
gg <- g+geom_density(aes(x = Xtd, y = ..density..,fill = Treatment), stat = "density",alpha = 0.25, position="jitter")
gg <- gg+geom_vline(xintercept = mean(dtPlot[Treatment=="Control",Xtd]), color = "red", size = 2, alpha=.25)
gg <- gg+geom_vline(xintercept = mean(dtPlot[Treatment=="Treatment",Xtd]), color = "lightblue", size = 2, alpha=.5)
gg + labs(title = "Density Distribution of Landing Location (Xtd)", 
          subtitle = paste(" (N=", dtPlot[,.N]," Runs)",sep=""), 
          x = "Xtd", y = "Density", fill = "")

```

### Go Around Liklihood  
The following graph shows the difference in the go-around rate between treatment and control.  The difference is small.  The treatment group went around `r dt[Treatment == "Treatment" & Go.Around.==TRUE,.N]`, while the control went around `r dt[Treatment == "Control" & Go.Around.==TRUE,.N]`. 

```{r Go-Around_Dist, echo=FALSE}
dtPlot = dt[,.(Xtd, Treatment, Go.Around.)]

g <- ggplot(dtPlot)
gg <- g+geom_bar(aes(x = Go.Around., fill = Treatment), stat= "count", position = "dodge",alpha = 0.25, size = 2)

gg + labs(title = "Frequency of Go Around by Treatment", 
          subtitle = paste(" (N=", dtPlot[,.N]," Runs)",sep=""), 
          x = "Go Around", y = "Frequency", fill = "")

```



