---
title: "Practice Visual Priming"
author: "Dave Yachabach"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(data.table)
require(ggplot2)
```

## Practice Statistical Analysis for Visual Priming Experiment

This document describes a statistical analysis of simulated data.  The data simulates the performance of airline crews flying approach scenarios in a Level D 737 flight simulator.  For a description of the experiment see *Rethinking Runway Safety from the Bottom Up*.  See the codebook for a description of variables and tables.  


## Data Description  
The operational data for this practice analysis is in a practice data file.  The available files are:  

- *PD_4-21-2021.csv*.  

The simulated Roster data is in a Roster file.  The available files are:  

- *Roster_4-21-2021*  

```{r LoadData, echo=FALSE}

pthData <- "C:/Users/yacha/OneDrive/Education/Personal Interests/Aviation Research Interests/Visual Priming Experiment/Software/Practice Visual Priming Analysis/Data/"

filData <- paste(pthData,"PD_4-21-2021.csv", sep = "")
dt <- fread(filData, skip = 1, blank.lines.skip = TRUE, check.names = TRUE)

filData <- paste(pthData,"Roster_4-21-2021.csv", sep = "")
dtRoster <- fread(filData, skip = 1, blank.lines.skip = TRUE, check.names = TRUE)

```

### Independence of RunIDs  
The following graphs indicate that RunIDs were evenly distributed throughout a simulator session.  In other words, RL-NI was just as likely to occur on the 6th run as on the 15th run.



```{r RunID_Independence, echo=FALSE}



```

### Landing Accuracy  
Starting with landing accuracy, we will show the frequency distribution of the population, the treatment sample, and the control sample.  

```{r Xtd_Distribution}

dtPlot = dt[Go.Around.==FALSE,.(Xtd, Treatment)]

g <- ggplot(dtPlot)
gg <- g+geom_histogram(aes(x = Xtd, fill = Treatment), bins = 10, alpha = 0.5)
gg + labs(title = "Frequency of Landing Location (Xtd)", 
          subtitle = paste(" (N=", dtPlot[,.N]," Runs)",sep=""), 
          x = "Xtd", y = "Frequency", fill = "")

```


